Disambiguating Monocular Depth Estimation with a Single Transient

### 2020-03-05 paper/eccv2020/sections/discussion.tex
pass over discussion

\edit{In the diffuse setting, the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light will return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited
to short to medium-range scenes.} \edit{Nevertheless, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
diffuse scene at $r = 2$ m
and a field of view of $\theta = 40^\circ$ can be calculated as}
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation} 
\edit{giving $P_{\text{min}}=21$ mW, less than the 60 mW of the Kinect.}

\edit{Under these scene parameters, we can compute the total incident 
  flux on the SPAD per second (derived in~\cite{mcmanamon2012ladar}) as}
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
  \end{equation}
  \edit{where $P_T$ is the illumination power in the visible region, $\rho$ is its
  albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to
  the object, and $\eta$ is the quantum efficiency of the detector. For nominal
  values of these quantities, and a laser pulse repitition rate of 10 MHz, we find that the number of photon detections is well
  above the threshold required to assume the low-flux condition (roughly 1-5\%
  of the number of illuminations per second~\cite{oconnortcspc}).
  } \edit{Given this high incident photon count, we would envision using an optical
    element such as an aperture or neutral density filter to return to the
    low-flux regime, or use a pile-up correction technique~\cite{Heide:2018}.}

  \edit{Lastly, Figure~\ref{fig:hardware}(b)-(c) empirically shows that in the
  low-flux regime, collecting and summing scanned
measurements is nearly identical to capturing diffused measurements. ?!We show
empirical comparisons between the two modes on a more complex scene in the supplement?!}

>>>>

\edit{In the diffuse setting, the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light will return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited
to short to medium-range scenes with a reasonable power budget for the diffused
illumination.} \edit{For example, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
diffuse scene at $r = 2$ m
and a field of view of $\theta = 40^\circ$ can be calculated as}
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation} 
\edit{giving $P_{\text{min}}=21$ mW. We note that this is significantly 
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.}

\edit{Under these scene parameters, we can compute the total incident 
  flux on the SPAD per second (derived in~\cite{mcmanamon2012ladar}) as}
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
  \end{equation}
  \edit{where $P_T$ is the illumination power in the visible region, $\rho$ is its
  albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to
  the object, and $\eta$ is the quantum efficiency of the detector. For a range of 
  values similar to those of our experiments (detailed in the supplement), we find that
  the ratio of photon detections to illumination pulses is roughly 4\%, or well within 
  low-flux regime where pileup is negligible~\cite{oconnortcspc}.
  We also empirically validate that our method works with a diffused setup and an output power of 
  approximately 25 mW without significant pileup effects as detailed in the supplement.
  } \edit{However, even for operation in the high-flux regime, pileup can be mitigated  
    by reducing the amount of incident light, for example by reducing the aperture size or 
    using neutral density filters, or by using a pile-up correction technique~\cite{Heide:2018}.}

### 2020-03-05 paper/eccv2020/sections/hardware.tex
Added discussion about the the two spad histograms
pass over discussion

\edit{To verify that our simulated diffused SPAD measurements are equivalent to measurements produced by an actual diffused SPAD, we setup a system consisting of a diffused and scanned SPAD side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the diffuse SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate the two systems produce near equivalent measurements; the slight differences in their two histograms can be attributed to a baseline difference of about 10cm. That is, they see the scene from slightly different perspectives.
}

>>>>

\edit{To verify that our simulated diffused SPAD measurements match measurements produced by an actual diffused SPAD, we set up a system consisting of a diffused and scanned SPAD side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems produce near equivalent measurements. Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions. That is, they observe scene from slightly different perspectives.
}
